---
title: "Collate scores"
output: html_notebook
---

Pull genetics and genomics scores for MSN

```{r}
synapser::synLogin()
msnObj<-synapser::synGet('syn21652325')
msn <- data.table::fread(msnObj$path,data.table=F)
msn <- msn[,-1]
```

Pull genetics and genomics scores for Retromer
```{r}
synapser::synLogin()
retromerObj<-synapser::synGet('syn21652323')
retromer <- data.table::fread(retromerObj$path,data.table=F)
retromer <- retromer[,-1]
```

Pull genetics and genomics scores for smoc1
```{r}
synapser::synLogin()
smoc1Obj<-synapser::synGet('syn21740156')
smoc1<- data.table::fread(smoc1Obj$path,data.table=F)
smoc1 <- smoc1[,-1]
```

Pull genetics and genomics scores for pQTL
```{r}
synapser::synLogin()
pqtlObj<-synapser::synGet('syn21739428')
pqtl <- data.table::fread(pqtlObj$path,data.table=F)
pqtl <- pqtl[,-1]
```


Push raw data to synapse project for reference data (syn21534582)
```{r}
#library(dplyr)
#synapser::File('data/OPEN-AD.literature.030220.xlsx',parent='syn21534582') %>% synapser::synStore()
#synapser::File('data/OPEN-AD.literature.030220b.pptx',parent='syn21534582') %>% synapser::synStore()
#synapser::File('data/OPENAD_02172020.pdf',parent='syn21534582') %>% synapser::synStore()
#synapser::File('data/OPENAD_Fly_Validation_030420.xlsx',parent='syn21534582') %>% synapser::synStore()
```

pull down literature and reformat appropriately
```{r}
literatureObj <- synapser::synGet('syn21724349')
noveltyMetric <- readxl::read_excel(literatureObj$path,sheet='ADassociationsPerYear')
pubsLastFiveYears <- colSums(noveltyMetric[37:41,-1])
totalPubs <- colSums(noveltyMetric[,-1])
appPubs <- totalPubs[15]

recency<-pubsLastFiveYears/totalPubs
recency[totalPubs<=10]<- 1

literatureScore <- (1 - log10(totalPubs+1)/log10(appPubs+1))
literatureScore <- literatureScore*recency*2

litScoreDf <- data.frame(Gene=names(literatureScore),
                         litScore=literatureScore,
                         stringsAsFactors=F)
#View(litScoreDf)

```


pull down fly neuropath and reformat appropriately (syn21724443)

```{r}
flynpObj <- synapser::synGet('syn21724443')
flynp <- readxl::read_excel(flynpObj$path,sheet='Sheet1')
flynp$FlyNeuroPathScore <- (flynp$Score/max(flynp$Score))*2
flynp <- dplyr::select(flynp,`Human Gene`,`Fly Homolog`,'FlyNeuroPathScore')
```


Combine into a single data frame and push to synapse with provenance.

```{r}
msn <- dplyr::select(msn,-overall)
retromer <- dplyr::select(retromer,-overall)
smoc1 <- dplyr::select(smoc1,-overall)
pqtl <- dplyr::select(pqtl,-overall)
msn$pathway <- 'MSN'
retromer$pathway <- 'Endosomal'
smoc1$pathway <- 'SMOC1'
pqtl$pathway <- 'pqtl'
targetDf <- rbind(msn,retromer,smoc1,pqtl)
targetDf <- dplyr::left_join(targetDf,
                             litScoreDf,
                             by=c('GeneName'='Gene'))
targetDf <- dplyr::left_join(targetDf,
                             flynp,
                             by=c('GeneName'='Human Gene'))
targetDf$OverallScore <- rowSums(dplyr::select(targetDf,
                                               'Omic_score',
                                               'Genetic_score',
                                               'litScore',
                                               'FlyNeuroPathScore'),na.rm=T)

targetDf <- dplyr::arrange(targetDf,dplyr::desc(OverallScore))
colnames(targetDf)[which(colnames(targetDf)=='Fly Homolog')] <- 'Fly_Homolog'
targetDf <- dplyr::select(targetDf,
                          GeneName,
                          Fly_Homolog,
                          pathway,
                          Genetic_score,
                          Omic_score,
                          litScore,
                          FlyNeuroPathScore,
                          OverallScore)



```




download druggability
```{r}
fooObj <- synapser::synGet('syn13363443')
druggability <- data.table::fread(fooObj$path,data.table=F)
geneTable <- utilityFunctions::convertEnsemblToHgnc(druggability$GeneID)
druggability <- dplyr::left_join(druggability,geneTable,by=c('GeneID'='ensembl_gene_id'))
```


join with target matrix
```{r}
targetDf <- dplyr::left_join(targetDf,druggability,by=c('GeneName'='external_gene_name'))
write.csv(targetDf,file='data/OPENADTargetScores.csv',quote=F,row.names=F)
```



```{r}
foo <- synapser::File('data/OPENADTargetScores.csv',
                      parent='syn21739107')
foo <- synapser::synStore(foo,
                          used = c('syn21652325','syn21652323','syn21724349','syn21724443','syn21740156','syn21739428','syn13363443'),
                          executed = 'https://github.com/blogsdon/OPENADBCScoring/blob/ba45915bcab587e68e31780b58366c7d7ff0d12b/collateScores.Rmd')
```

